---
title: "Codebook"
author: "Ahmed Zoha"
date: "September 16, 2015"
output: html_document
---
This ***Code Book*** is generated on `r as.character(Sys.time())`, for the Coursera "Getting and Cleaning Data" course project. The description of the variables found in the tidy dataset is as follows:

Variable Description
---------------------


Variable name    | Description
-----------------|------------
subject          | It specifies the subject ID who has performed the activity. The value ranges from 1 to 30.
activity         | Name of the Activity 
featcategories   | Feature: It shows the categorization whether it is Time domain signal or frequency domain signal (i.e., Time or Freq)
featint          | Feature: Specifies the Measuring instrument (i.e., Accelerometer or Gyroscope)
featAcc          | Feature: Acceleration signal (Body or Gravity)
featstat         | Feature: Statistics (i.e., Mean or Standard Deviation (SD))
fJerk            | Feature: Jerk signal
fMagnitude       | Feature: Magnitude of the signals 
fAxis            | Feature: It specifies the axis of the 3-axial signals (i.e., X, Y, or Z direction)
count            | Feature: Count of data points used to compute `average`
average          | Feature: Average of each variable for each activity and each subject

Structure of the Dataset
-----------------

```{r}
str(dftidy)

```
Key variables in the data table
----------------------------------------

```{r}
key(dftidy)
```

Displaying First 10 rows of the Dataset
---------------------------------------

```{r}
head(dftidy,n=10)
```

Summary
-------

```{r}
summary(dftidy)
```
Save to file
------------

Save the dataframe `dftidy` to  `tidydataset.txt`.

```{r save}
f = file.path(pathdata, "tidaydataset.txt")
write.table(dftidy, f, quote=FALSE, sep="\t", row.names=FALSE)
```
